Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-05-13 paper/main.tex
reduced abstract length

\begin{abstract}

We study the alignment of dark matter halos with the cosmic web
characterized by the tidal and velocity shear fields. We focus on the
alignment of their shape, angular momentum and peculiar velocities. We  
use a cosmological N-body simulation that allows to study dark matter
halos spanning almost five orders of magnitude in mass
($10^{9}$-$10^{14}$) \hMsun and use spatial scales of
$(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the halo shape
presents the strongest alignment along the smallest tidal eigenvector,
e.g. along filaments and walls, with a signal that gets stronger as
the halo mass increases. In the case of the velocity shear field only 
massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
the largest tidal eigenvector; that is perpendicular to filaments and
walls. For the angular momentum we find alignment signals only for
halos more massive than $10^{12}$\hMsun both in the tidal and velocity
shear webs where the preferences are for it to be parallel to the
middle eigenvector; perpendicular to filaments and parallel to
walls. Finally, the peculiar velocities show a strong alignment along
the smallest tidal eigenvector for all halo masses; halos move along filaments
and walls. In the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}\hMsun$. Most of
the different signals between the two web descriptions are due to the
fact that the main directions of stronger tidal tension and velocity
shear coincide for halos below $10^{12}$\hMsun but are perpendicular
to each other for halos more massive than this threshold.  Our results
clearly show that the two different algorithms we used to define the
cosmic web describe different physical aspects of non-linear collapse
and should be used in a complementary way to understand the effect of
the cosmic web on galaxy evolution. 
\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter, large-scale structure of Universe
\end{keywords}

>>>>

\begin{abstract}
We study the alignment of dark matter halos with the cosmic web
characterized by the tidal and velocity shear fields. We focus on the
alignment of their shape, angular momentum and peculiar velocities. We  
use a cosmological N-body simulation that allows to study dark matter
halos spanning almost five orders of magnitude in mass
($10^{9}$-$10^{14}$) \hMsun and spatial scales of
$(0.5$-$1.0)$\hMpc to define the cosmic web. We find that the halo shape
presents the strongest alignment along the smallest tidal eigenvector,
e.g. along filaments and walls, with a signal that gets stronger as
the halo mass increases. In the case of the velocity shear field only 
massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
the largest tidal eigenvector; that is, perpendicular to filaments and
walls. For the angular momentum we find alignment signals only for
halos more massive than $10^{12}$\hMsun both in the tidal and velocity
shear webs where the preferences are for it to be parallel to the
middle eigenvector; perpendicular to filaments and parallel to
walls. Finally, the peculiar velocities show a strong alignment along
the smallest tidal eigenvector for all halo masses; halos move along filaments
and walls. In the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}\hMsun$. Our
results clearly show that the two different algorithms we used to
define the cosmic web describe different physical aspects of
non-linear collapse and should be used in a complementary way to
understand the effect of the cosmic web on galaxy evolution.    
\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter, large-scale structure of Universe
\end{keywords}
